% Key Findings Summary for CHI 2025 Paper
% Main insights from statistical text analysis

\section{Key Findings Summary}

\subsection{Primary Research Contributions}

\begin{enumerate}

\item \textbf{Evaluation frameworks systematically influence moral reasoning}: Statistical analysis of 1,313 professional explanations provides the first quantitative evidence that evaluation tools shape not just measurement, but the underlying reasoning patterns of UX professionals.

\item \textbf{Ethical metrics enhance manipulation detection}: Participants exposed to ethical evaluation dimensions (UEEQ condition) showed 16.7\% manipulation awareness compared to 0\% in traditional UX metrics (UEQ) and 3.5\% in business context only (RAW). Effect size: Cramér's V = 0.289 (large effect).

\item \textbf{Absence of metrics promotes responsibility avoidance}: RAW condition participants showed 5× higher rates of responsibility delegation (5.5\%) compared to conditions with quantitative guidance (~1\%). Effect size: Cramér's V = 0.137 (medium effect).

\item \textbf{Industry conformity emerges as decision heuristic}: When lacking specific evaluation criteria, 2.7\% of RAW participants justified decisions through industry precedent (``common interface,'' ``follows other social media giants''), compared to 0\% in other conditions.

\item \textbf{Framework-specific reasoning patterns}: Each evaluation approach produced distinct professional discourse patterns, from data-driven argumentation (UEQ/UEEQ) to institutional authority appeals (RAW).

\end{enumerate}

\subsection{Statistical Evidence}

All five reasoning patterns showed significant differences across conditions (p < 0.01):
\begin{itemize}
\item \textbf{Manipulation Awareness}: χ² = 109.424, p < 0.001, V = 0.289
\item \textbf{Responsibility Avoidance}: χ² = 24.508, p < 0.001, V = 0.137  
\item \textbf{Industry Conformity}: χ² = 15.307, p < 0.001, V = 0.139
\item \textbf{Aesthetic Focus}: χ² = 14.011, p < 0.001, V = 0.116
\item \textbf{Emotional Reaction}: χ² = 9.554, p = 0.008, V = 0.086
\end{itemize}

\subsection{Implications for Design Practice}

\begin{itemize}
\item \textbf{Tool design matters}: Evaluation frameworks are not neutral measurement instruments—they actively shape professional judgment and ethical sensitivity.

\item \textbf{Need for ethical evaluation integration}: Traditional UX metrics fail to promote ethical reasoning, while explicit ethical dimensions dramatically improve manipulation recognition.

\item \textbf{Responsibility diffusion risk}: Business-context-only decision making promotes authority delegation rather than professional ethical judgment.

\item \textbf{Framework-aware education}: Design education should address how different evaluation approaches influence moral reasoning patterns.
\end{itemize}

\subsection{Example Quotes Illustrating Key Patterns}

\textbf{Manipulation Awareness (UEEQ):}
\begin{quote}
\textit{``I would not release this interface because it is fundamentally deceptive: it tells users their geolocation is off while still using their location data. The deception score of -1.76 shows users find it highly dishonest.''}
\end{quote}

\textbf{Responsibility Avoidance (RAW):}
\begin{quote}
\textit{``Given that the business team, marketing department, and my supervisor have all approved the design...withholding my final approval would be a significant professional and business risk.''}
\end{quote}

\textbf{Industry Conformity (RAW):}
\begin{quote}
\textit{``Common interface! Great UI, follows similarly to other social media giants.''}
\end{quote}
