% Proposed CHI 2025 Abstract - Merged insights from original UEEQ work and three-condition experiment

User experience (UX) evaluation frameworks fundamentally shape how designers perceive and make decisions about interface designs, yet their influence on ethical design judgment remains largely unexplored. Through a three-condition experiment with 141 UX professionals, we demonstrate that the lens through which designers interpret user feedback systematically affects their willingness to implement interfaces containing dark patterns. 

Participants evaluated dark pattern interfaces under three conditions: viewing standard User Experience Questionnaire (UEQ) data, viewing UEQ data enhanced with autonomy-focused metrics, or making decisions without evaluation data. Results revealed a clear progression: designers were most accepting of dark patterns when viewing standard UEQ metrics (release tendency M=3.80), moderately critical with no evaluation framework (M=4.66), and most critical when presented with autonomy-enhanced evaluation data (M=3.14). Effect sizes were substantial (d=0.56 to 1.20), with rejection rates nearly doubling from 30% to 56% between no-evaluation and autonomy-focused conditions.

Six specific dark patterns showed significant sensitivity to evaluation framework, including content customization (d=1.02) and endlessness patterns (d=0.73). These findings suggest that standard UX metrics may inadvertently legitimize manipulative design by emphasizing usability and satisfaction while obscuring ethical concerns. Conversely, evaluation frameworks that foreground user autonomy significantly increase designers' sensitivity to manipulation.

This work reveals a critical gap in current UX practice: the tools we use to measure "good" design may systematically bias us toward accepting harmful patterns. We contribute empirical evidence that evaluation frameworks are not neutral measurement tools but active influences on ethical design decision-making, calling for more intentional development of assessment methods that align with broader societal values.

% Keywords: Dark Patterns, User Experience Evaluation, Ethical Design, Design Decision-Making, UX Metrics
